\documentclass[margin,line]{resume}

\begin{document}
\name{\Huge Michael J. Lawson}
\begin{resume}

\section{\mysidestyle Contact\\Information}
    P.O. Box 3202   					  \hfill Phone: 401-267-8709 \\
    Boulder, CO 80307                  \hfill E-mail: michael.lawson@nrel.gov

\section{\mysidestyle Objective}
    To obtain a research position where I can use my computational and experimental fluid dynamics expertise to study marine hydrokinetic energy devices.

\section{\mysidestyle Education}
    \textbf{Ph.D. in Mechanical Engineering}, The Pennsylvania State University, 2010 \\
    \emph{Advisors:}  Dr. Gary Settles and Dr. Eric Paterson \\
    \emph{Dissertation:} A Fundamental Study of the Airflow and Odorant Transport Phenomena of Canine Olfaction
    \vspace{3mm}\\
    \textbf{M.S. in Mechanical Engineering}, Virginia Tech, 2006 \\
    \emph{Advisor:}  Dr. Karen Thole\\
    \emph{Thesis:} Practical Applications of Delta Winglets in Compact Heat Exchangers with Louvered Fins
    \vspace{3mm}\\
    \textbf{B.S. in Mechanical Engineering}, Virginia Tech, 2005 \\
    \emph{Minor:}  Mathematics

\section{\mysidestyle Experience}
    \textbf{National Renewable Energy Laboratory -- Wind Technology Center}\\
    Boulder, CO, Sep. 2010 -- Present  \\
    \emph{Position:} Post-Doctoral Researcher\vspace{-3mm}\\\vspace{-1mm}%
    \begin{list2}
        \item Designed and analyzed a tidal current turbine and an ocean current turbine as part of the DOE Reference Model Project
        \item Developed a time-domain simulation tool to model wave energy converters with an NREL research team
        \item Developed a new version of the axial-flow rotor optimization code HARP-Opt
        \item Studied the pressure fields experienced by Bat's as they fly near wind turbine blades using CFD simulations and used the results to evaluate the theory that Bat's are dying from barotrauma (i.e. low pressures around the blades)
	    \item Developed computational fluid dynamics (CFD) methods to simulate tidal current turbines        
        \item Developed a discrete vortex method code to simulate vertical axis turbines
        \item Worked with a summer intern to develop a wave energy converter power-take-off model in the open-source CFD code OpenFOAM
    \end{list2}\vspace{-1.5mm}
    \textbf{Penn State Gas Dynamics Lab and U.S. Navy Applied Research Lab}\\
    University Park, PA, Jan. 2007 -- Sep. 2010  \\
    \emph{Position:} National Defense Science and Engineering Graduate Fellow\vspace{-3mm}\\\vspace{-1mm}%
    \begin{list2}
        \item Investigated the fluid dynamics and chemical transport phenomena involved in canine olfaction for a project funded by DARPA and the U.S. Transportation Security Laboratory
        \item Developed a multi-phase CFD model for simulating odorant transport and deposition in the canine nasal airways using the open-source CFD code OpenFOAM
        \item Designed and fabricated a model of the canine nasal cavity using rapid prototyping techniques for use in flow visualization experiments
        \item Designed aerodynamic sampling devices to improve electronic nose performance
        \item Developed seedless particle image velocimetry (PIV) techniques using Schlieren optics for use in compressible flows
    \end{list2}\vspace{-1.5mm}
    \textbf{BMW Aerodynamics Division}\\
    Munich, Germany, May 2006 -- Jan. 2007\\
    \emph{Position:} Graduate Research Assistant\vspace{-3mm}\\\vspace{-1mm}%
        \begin{list2}
        \item Performed vehicle aerodynamics research using CFD techniques
        \item Simulated under-hood flows with the goal of improving engine block cooling while simultaneously reducing drag
    \end{list2}\vspace{-1.5mm}
    \textbf{Virginia Tech Experimental and Computational Combustion Lab}\\
    Blacksburg, VA, July 2005 -- May. 2006\\
    \emph{Position:} Graduate Research Assistant\vspace{-3mm}\\\vspace{-1mm}%
        \begin{list2}
        \item Developed a method to enhance heat exchanger efficiency using vortex generators
        \item Evaluated different heat exchanger designs using experimental and computational methods
    \end{list2}\vspace{-1.5mm}
    \textbf{Rolls Royce Aero Engines}\\
    Blacksburg, VA, Sep. 2004 -- May. 2005\\
    \emph{Position:} Undergraduate Researcher\vspace{-3mm}\\\vspace{-1mm}%
        \begin{list2}
        \item Designed and constructed a test-rig to study the influence of stator-rotor gap geometry on turbine blade cooling performance
    \end{list2}\vspace{-1.5mm}

\section{\mysidestyle Journal\\Publications}
    \textbf{Houck, D., Lawson, M., and Thresher, R.}, 2012. ``A Computational Study of Pressures Experienced by Bats Flying Near Wind Turbine Blades: Implications for Barotrauma''. \emph{In Preparation}.
    \vspace{1.5mm}
    \\
    \textbf{Lawson, M., Craven, B., Paterson, E., and Settles, G.}, 2012. ``A Computational Study of Odorant Transport and Deposition in the Canine Nasal Cavity: Implications for Olfaction". \emph{Chemical Senses}, 37 (6), pp. 553-566.
    \vspace{1.5mm}
    \\
    \textbf{Lawson, M., Craven, B., Paterson, E., and Settles, G.}, 2012. ``An Experimental Study of Airflow Patterns in an Anatomically-correct Model of the Canine Nasal Cavity". \emph{Experiments in Fluids (In Preparation)}.
    \vspace{1.5mm}
    \\
    \textbf{Hargather, M., Lawson, M., Settles, G., and Weinstein, L.}, 2011. ``Seedless Velocimetry Measurements by Schlieren Image Velocimetry". \emph{American Institute of Aeronautics and Astronautics Journal}, 49 (3), pp. 611-620.
    \vspace{1.5mm}
    \\
    \textbf{Craven, B., Paterson, E., Settles, G., and Lawson, M.}, 2009. ``Development and Verification of a High-fidelity Computational Fluid Dynamics Model of Canine Nasal Airflow". \emph{Journal of Biomechanical Engineering}, 131, pp. 091002.
    \vspace{1.5mm}
    \\
    \textbf{Lawson, M., and Thole, K.}, 2008. ``Heat Transfer Augmentation Along the Tube Wall of a Louvered Fin Heat Exchanger Using Practical Delta Winglets". \emph{International Journal of Heat and Mass Transfer}, 51(9-10), pp. 2346–-2360.

\section{\mysidestyle Conference\\Publications}
    \textbf{Lawson, M., Li, Y., and Sale, D.}, 2011. ``Development and Verification of a Computational Fluid Dynamics Model of a Horizontal-axis Tidal Current Turbine". No. OMAE2011-49863, \emph{Proceedings of the 30th International Conference on Ocean, Offshore, and Arctic Engineering}.
    \vspace{1.5mm}
    \\
    \textbf{Bir, G., Lawson, M., and Li, Y.}, 2011. ``Structural Design of a Horizontal-axis Tidal Current Turbine Composite Blade". No. OMAE2011-50063, \emph{Proceedings of the 30th International Conference on Ocean, Offshore, and Arctic Engineering}.
    \vspace{1.5mm}
    \\
    \textbf{Hargather, M., Lawson, M., Settles, G., Weinstein, L., and Gogineni, S.}, 2009. ``Focusing-Schlieren PIV Measurements of a Supersonic Turbulent Boundary Layer". No. AIAA 2009-69, \emph{47th AIAA Aerospace Sciences Meeting Including The New Horizons forum and Aerospace Exposition}.
    \vspace{1.5mm}
    \\
    \textbf{Lawson, M., Sanders, P., and Thole, K.}, 2006. ``Computational and Experimental Comparison of Tube Wall Heat Transfer Augmented by Winglets in Louvered Fin Heat Exchangers". No. IMECE2006-14452, \emph{ASME 2006 International Mechanical Engineering Congress and Exposition}, pp. 681–-691.

\section{\mysidestyle Conference\\Presentations}
    \textbf{Lawson, M.}, 2010. ``Simulating Conjugate Scalar Transport in the Dog's Nose", \emph{Mid-Atlantic OpenFOAM Users Group Meeting}.
    \vspace{1.5mm}
    \\
    \textbf{Lawson, M., Paterson, E., and Settles, G.}, 2010. ``A Computational Study of Odorant Transport During Canine Olfaction", \emph{U.S. National Committee on Theoretical and Applied Mechanics}.
    \vspace{1.5mm}
    \\
    \textbf{Lawson, M., Paterson, E., and Settles, G.}, 2009. ``Odorant Transport and Deposition in the Canine Nasal Airways", \emph{American Physics Society - Division of Fluid Dynamics Conference}.
    \vspace{1.5mm}
    \\
    \textbf{Lawson, M., Paterson, E., and Settles, G.}, 2009. ``Flow Visualization Experiments In A 4:1 Scale Model of The Canine Nasal Cavity", \emph{American Physics Society - Division of Fluid Dynamics Conference}.
    \vspace{1.5mm}
    \\
    \textbf{Lawson, M., and Settles, G.}, 2007. ``Focusing-schlieren PIV for the measurement of 3-D turbulent flows", \emph{American Physics Society - Division of Fluid Dynamics Conference}.
    \vspace{1.5mm}
    \\
    \textbf{Settles, G., Lawson, M., Hargather, M., and Bigger, R.}, 2007. ``Belt-Snap and Towel-snap Shock Waves", \emph{American Physics Society - Division of Fluid Dynamics Conference}.

\section{\mysidestyle Technical\\Reports}
    \textbf{Beam, M., Kline, B., Elbing, B., Fontaine A., Lawson M., Thresher, R., and Li, Y}, 2012. ``Marine Hydrokinetic Turbine Power-Take-Off Design for Optimal Performance and Low Impact on Cost-of-Energy", \emph{NREL Report No. CP-5000-54410.}.
    \vspace{1.5mm}
    \\
    \textbf{Lawson, M., Bir, G., and Thresher, R.}, 2012. ``The Development of a Preliminary Design for a Horizontal Axis Tidal Current Turbine", \emph{NREL Report (Under Internal Review)}.
    
\section{\mysidestyle Peer-Reviewer}
    \textbf{Renewable Energy \\
    Experiments in Fluids\\
    International Journal of Heat and Fluid Flow\\
    International Journal of Thermal Sciences\\
    Journal of Biomechanics\\
    International Conference on Ocean, Offshore, and Arctic Engineering (OMAE) \\
    American Institute of Aeronautics and Astronautics Wind Energy Symposium}

\section{\mysidestyle Technical\\Skills}
    \textbf{Computational fluid dynamics expertise:} RANS, Scalar transport, Multiphase Navier-Stokes, Discrete vortex methods, Boundary element methods\\
    \textbf{CFD software competency:} OpenFOAM, Acusolve, Fluent, STAR--CD, STAR--CCM+, ICEM, Harpoon, Pointwise, SnappyHexMesh, OrcaFlex\\
    \textbf{Programming languages:} C/C++, Python, FORTRAN, MATLAB, LabVIEW, Shell scripting\\
    \textbf{Visualization software:} TecPlot, Paraview, EnSight\\
    \textbf{Operating systems:} Linux, Mac OSX, Windows
    \textbf{Experimental methods:} Wind tunnel experience, PIV, Schlieren, Shadowgraph, Flow visualization (in air and water), High-speed videography

\section{\mysidestyle Security\\Clearance}
    \textbf{Secret Security Clearance}\\
    Granted by the US Department of the Navy, 2008 - 2010
    %\newpage

\section{\mysidestyle References}
%    \textbf{Dr. Gary S. Settles}                            \\
%    Distinguished Professor                                 \\
%    Department of Mechanical and Nuclear Engineering        \\
%    The Pennsylvania State University                       \\
%    301D Reber Building, University Park, PA, 16802         \\
%    Phone: 814-863-1504                                     \\
%    E-mail: gss2@psu.edu
%    \vspace{3mm}\\
%    \textbf{Dr. Eric G. Paterson}                                       \\
%    Department Head and Professor       \\
%    Aerospace and Ocean Engineering                     \\
%    Virginia Tech                                  \\
%    215 Randolph Hall 0203, Blacksburg, VA 24061                 \\
%    Phone: 540-231-2314                                                \\
%    E-mail: egp@vt.edu
%    \vspace{3mm}\\
%    \textbf{Dr. Karen A. Thole}                                         \\
%    Department Head and Professor                                       \\
%    Department of Mechanical and Nuclear Engineering                    \\
%    The Pennsylvania State University                                   \\
%    136 Reber Building, University Park, PA 16802                       \\
%    Phone: 814-865-2519                                                 \\
%    E-mail: kthole@psu.edu
%    \vspace{3mm}\\
%    \textbf{Dr. Robert W. Thresher}                                         \\
%    Research Fellow                                       \\
%    National Wind Technology Center	\\
%    National Renewable Energy Laboratory                                 \\
%    1617 Cole Blvd. MS 3811, Golden, CO 80401                  \\
%    Phone: 303-384-6922                                                 \\
%    E-mail: robert.thresher@nrel.gov
Available upon request

\end{resume}
\end{document}
