%\vspace{-0.2in}
\subsubsection*{Conference Publications}
\vspace{-0.15in}

\begin{enumerate}[leftmargin=1.5pc,itemsep=0pt,parsep=0pt,topsep=0pt,partopsep=1pt]

\item \textbf{Lawson, M., Barahona Garzon, B., Wendt, F., Yu, Y., Michelen, C.}, 2016. ``COER Hydrodynamic Modeling Competition: Modeling the Dynamic Response of a Floating Body Using the WEC-Sim and FAST Simulation Tools''. \emph{Proceedings of the ASME 35th International Conference on Ocean, Offshore and Arctic Engineering}, Paper No. OMAE2015-42288.

\item \textbf{Tom N., Yu, Y., Wright, A., Lawson, M.}, 2016. ``Balancing Power Absorption and Fatigue Loads in Irregular Waves for an Oscillating Surge Wave Energy Converter''. \emph{Proceedings of the ASME 35th International Conference on Ocean, Offshore and Arctic Engineering}, Paper No. OMAE2016-55046.

\item \textbf{Quon, E., Platt, A., Yu, Y., Lawson, M.}, 2016. ``Application of the Most Likely Extreme Response Method for Wave Energy Converters''. \emph{Proceedings of the ASME 35th In- ternational Conference on Ocean, Offshore and Arctic Engineering}, Paper No. OMAE2016-54751.

\item \textbf{Tom N., Lawson, M., Yu, Y.}, 2015. ``Recent Additions in the Modeling Capabilities of an Open-Source Wave Energy Converter Design Tool''. \emph{Proceedings of the Twenty-Fifth International Ocean and Polar Engineering Conference}, pp. 835-842.

\item \textbf{Yu, Y., Van Rij, J., Coe, R., Lawson, M}, 2015. ``Preliminary Wave Energy Convert- ers Extreme Load Analysis''. \emph{Proceedings of the ASME 34th International Conference on Ocean, Offshore and Arctic Engineering}, Paper No. OMAE2015-41532.

\item \textbf{Lawson, M., Yu, Y., Nelessen, A., Ruehl, K., Michelen, C}, 2014. ``Implementing Nonlinear Buoyancy and Excitation Forces in the WEC-Sim Wave Energy Converter Mod- eling Tool''. \emph{Proceedings of the ASME 33rd International Conference on Ocean, Offshore and Arctic Engineering}, Paper No. OMAE2014-24445.

\item textbf{Ruehl, K., Michelen, C., Kanner, S., Lawson, M., Yu, Y.}, 2014. ``Preliminary Verification and Validation of WEC-Sim, an Open-Source Wave Energy Converter Design Tool''. \emph{Proceedings of the ASME 33rd International Conference on Ocean, Offshore and Arctic Engineering}, Paper No. OMAE2014-XXXYYYZZZ

\item \textbf{Lawson, M., Li, Y., and Sale, D.}, 2011. ``Development and Verification of a Computational Fluid Dynamics Model of a Horizontal-Axis Tidal Current Turbine''. \emph{Proceedings of the 30th International Conference on Ocean, Offshore, and Arctic Engineering}, Paper No. OMAE2011-49863.

\item \textbf{Bir, G., Lawson, M., and Li, Y.}, 2011. ``Structural Design of a Horizontal-axis Tidal Current Turbine Composite Blade''. \emph{Proceedings of the 30th International Conference on Ocean, Offshore, and Arctic Engineering}, Paper No. OMAE2011-50063.

\item \textbf{Hargather, M., Lawson, M., Settles, G., Weinstein, L., and Gogineni, S.}, 2009. ``Focusing-Schlieren PIV Measurements of a Supersonic Turbulent Boundary Layer''. \emph{47th AIAA Aerospace Sciences Meeting Including The New Horizons forum and Aerospace Exposition}, Paper No. AIAA 2009-69

\item \textbf{Lawson, M., Sanders, P., and Thole, K.}, 2006. ``Computational and Experimental Comparison of Tube Wall Heat Transfer Augmented by Winglets in Louvered Fin Heat Exchangers''. \emph{ASME 2006 International Mechanical Engineering Congress and Exposition}, Paper No. IMECE2006-14452

\end{enumerate}




% Conference Publications
% Tom N., Yu, Y., Wright, A., Lawson, M., 2016. ``Balancing Power Absorption and Fatigue Loads in Irregular Waves for an Oscillating Surge Wave Energy Converter''. Proceedings of the ASME 35th International Conference on Ocean, Offshore and Arctic Engineering, Paper No. OMAE2016-55046.
% Quon, E., Platt, A., Yu, Y., Lawson, M., 2016. ``Application of the Most Likely Ex- treme Response Method for Wave Energy Convertersl''. Proceedings of the ASME 35th In- ternational Conference on Ocean, Offshore and Arctic Engineering, Paper No. OMAE2016- 54751.
% Lawson, M., Barahona Garzon, B., Wendt, F., Yu, Y., Michelen, C., 2016. ``COER Hydrodynamic Modeling Competition: Modeling the Dynamic Response of a Floating Body Using the WEC-Sim and FAST Simulation Tools''. Proceedings of the ASME 35th Interna- tional Conference on Ocean, Offshore and Arctic Engineering, Paper No. OMAE2015-42288.
% Tom N., Lawson, M., Yu, Y., 2015. ``Recent Additions in the Modeling Capabilities of an Open-Source Wave Energy Converter Design Tool''. Proceedings of the Twenty-Fifth International Ocean and Polar Engineering Conference, pp. 835-842.
% Yu, Y., Van Rij, J., Coe, R., Lawson, M, 2015. ``Preliminary Wave Energy Convert- ers Extreme Load Analysis''. Proceedings of the ASME 34th International Conference on Ocean, Offshore and Arctic Engineering, Paper No. OMAE2015-41532.
% Lawson, M., Yu, Y., Nelessen, A., Ruehl, K., Michelen, C., 2014. ``Implementing Nonlinear Buoyancy and Excitation Forces in the WEC-Sim Wave Energy Converter Mod- eling Tool''. Proceedings of the ASME 33rd International Conference on Ocean, Offshore and Arctic Engineering, Paper No. OMAE2014-24445.
% Ruehl, K., Michelen, C., Kanner, S., Lawson, M., Yu, Y., 2014. ``Preliminary Verification and Validation of WEC-Sim, an Open-Source Wave Energy Converter Design Tool''. Proceedings of the ASME 33rd International Conference on Ocean, Offshore and Arctic Engineering.
% Lawson, M., Li, Y., and Sale, D., 2011. ``Development and Verification of a Computa- tional Fluid Dynamics Model of a Horizontal-axis Tidal Current Turbine''. Proceedings of the 30th International Conference on Ocean, Offshore, and Arctic Engineering, Paper No. OMAE2011-49863.
% Bir, G., Lawson, M., and Li, Y., 2011. ``Structural Design of a Horizontal-axis Tidal Current Turbine Composite Blade''. Proceedings of the 30th International Conference on Ocean, Offshore, and Arctic Engineering, Paper No. OMAE2011-50063.
% Hargather, M., Lawson, M., Settles, G., Weinstein, L., and Gogineni, S., 2009. ``Focusing-Schlieren PIV Measurements of a Supersonic Turbulent Boundary Layer''. No. AIAA 2009-69, 47th AIAA Aerospace Sciences Meeting Including The New Horizons forum and Aerospace Exposition.
% Lawson, M., Sanders, P., and Thole, K., 2006. ``Computational and Experimental Comparison of Tube Wall Heat Transfer Augmented by Winglets in Louvered Fin Heat Exchangers''. No. IMECE2006-14452, ASME 2006 International Mechanical Engineering Congress and Exposition, pp. 681-691.
