\subsubsection*{\large{Technical Reports}}
\vspace{-0.15in}

\begin{enumerate}[leftmargin=1.5pc,itemsep=0pt,parsep=0pt,topsep=0pt,partopsep=1pt]

\item \textbf{Batty, H., Lawson, M.}, Planned Publication in 2018. U.S. ``Department of Energy Water Power Technologies Office: Strategy for Marine and Hydrokinetic (MHK) Technologies R\&D''.

\item \textbf{Yu, Y., Lawson, M., Li, Y., Previsic, M., Epler, J., Lou, J.}, 2015. ``Experimental Wave Tank Test for Reference Model 3 Floating-Point Absorber Wave Energy Converter Project'', Dept. of Energy Report DOE\/GO-102014-4450.

\item \textbf{V. Neary, M. Previsic, R. Jepsen, M. Lawson, Y. Yu, A. Copping, A. Fontaine, K. Hallett, D. Murray}, 2014. ``Methodology for Design and Economic Analysis of Marine Energy Conversion (MEC) Technologies''. SAND2014-9040

\item \textbf{Lawson, M., Yu, Y., Weber, J., Coe, R., Neary, V.}, 2014. ``Extreme Conditions Modeling Workshop Report'', Dept. of Energy Report, DOE\/GO-102014-4450.

\item \textbf{Musial, W., Lawson. M., Rooney, S.}, 2013. ``Marine and Hydrokinetic Technology (MHK) Instrumentation, Measurement, and Computer Modeling Workshop'', NREL Report NREL\/TP-5000-57605.

\item \textbf{Beam, M., Kline, B., Elbing, B., Fontaine A., Lawson M., Thresher, R., and Li, Y.}, 2012. ``Marine Hydrokinetic Turbine Power-Take-Off Design for Optimal Performance and Low Impact on Cost-of-Energy'', NREL Report No. CP-5000-54410.

\end{enumerate}

% Technical Reports
% Yu, Y., Lawson, M., Li, Y., Previsic, M., Epler, J., Lou, J., 2015. ``Experimental Wave Tank Test for Reference Model 3 Floating-Point Absorber Wave Energy Converter Project”, Dept. of Energy Report DOE/GO-102014-4450.
% Lawson, M., Yu, Y., Weber, J., Coe, R., Neary, V., 2014. ``Extreme Conditions Modeling Workshop Report”, Dept. of Energy Report DOE/GO-102014-4450.
% V. Neary, M. Previsic, R. Jepsen, M. Lawson, Y. Yu, A. Copping, A. Fontaine, K. Hallett, D. Murray (2014). Methodology for Design and Economic Analysis of Marine Energy Conversion (MEC) Technologies. SAND2014-9040
% Musial, W., Lawson. M., Rooney, S., 2013. ``Marine and Hydrokinetic Technology (MHK) Instrumentation, Measurement, and Computer Modeling Workshop”, NREL Report NREL/TP-5000-57605.
% Beam, M., Kline, B., Elbing, B., Fontaine A., Lawson M., Thresher, R., and Li, Y, 2012. ``Marine Hydrokinetic Turbine Power-Take-Off Design for Optimal Performance and Low Impact on Cost-of-Energy”, NREL Report No. CP-5000-54410.
% Lawson, M., Bir, G., and Thresher, R., 2012. ``The Development of a Preliminary De- sign for a Horizontal Axis Tidal Current Turbine”, NREL Report (Under Internal Review).
